---
#title: "Appendices"
#author: "Philip Joy"
output:
  word_document:
    #reference_docx: "rep_temp.docx"
    reference_docx: "figs_template.docx"
fontsize: 12pt
#date: "2025-05-23"
#always_allow_html: true

#knit: (function(input_file, encoding) {
#        rmarkdown::render(input_file, 
#                          output_file = paste0("RFsportmort_update_", "theModel_prelim_",Sys.Date(),".html"))
#      })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

getwd()
file.exists("../scripts/bayes_data_param_load.R")
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(ggplot2)
library(tidyverse)
library(wesanderson)
library(ggpubr)
library(knitr)
library(kableExtra)
library(here)
library(htmltools) 
library(coda)
library(jagsUI)
library(stringr)
library(readxl)
library(openxlsx2)
library(scales)
library(xlsx)
library(writexl)
library(readxl)

source("../scripts/mkdwn_functions.R", echo = FALSE)
#source("./scripts/bayes_data_param_load", echo = FALSE)
start_yr <- 1977
end_yr <- 2024
REP_YR <- 2024 #for Howard estimates
list2env(readinData(start_yr = start_yr,
                  end_yr = end_yr),
         .GlobalEnv)


mod<-"LB_fit_3pH"
res <- "Gen4int_indcomp_swhsR_FULL_pHB4pars_re0full_altwt_slepssquz_thru2024_6e+05__2025-11-09"

postH <- readRDS(paste0("..\\output\\bayes_posts\\",res,".rds"))

rhat <- get_Rhat(postH, cutoff = 1.11)

summary_table <- postH$summary %>%
  as.data.frame() %>%
  tibble::rownames_to_column(var = "Parameter") %>%
  select(Parameter, mean, sd, `2.5%`, `50%`, `97.5%`) %>%
  rename(
    Lower_CI = `2.5%`,
    Median = `50%`,
    Upper_CI = `97.5%`
  ) %>% 
  filter(str_detect(Parameter, "^tau_comp\\[") |
         str_detect(Parameter, "^tau_pH\\[") |
          str_detect(Parameter, "^mu_beta0_pelagic\\[")|
           str_detect(Parameter, "^tau_beta0_pelagic\\[")|
           str_detect(Parameter, "^mu_beta0_yellow\\[")|
           str_detect(Parameter, "^tau_beta0_yellow\\[")|
           str_detect(Parameter, "^mu_beta0_black\\[")|
           str_detect(Parameter, "^tau_beta0_black\\[")|
           str_detect(Parameter, "^mu_beta0_yellow_x\\[")|
           str_detect(Parameter, "^tau_beta0_yellow_x\\[")|
           str_detect(Parameter, "^mu_bc_H\\[")|
           str_detect(Parameter, "^tau_bc_H\\[")|
           str_detect(Parameter, "^mu_bc_R\\[")|
           str_detect(Parameter, "^tau_bc_R\\[")|
           str_detect(Parameter, "^bc_R_offset\\[")|
           str_detect(Parameter, "^beta0_pH\\[")|
           str_detect(Parameter, "^beta1_pH\\[")|
           str_detect(Parameter, "^beta2_pH\\[")|
           str_detect(Parameter, "^beta3_pH\\[")|
           str_detect(Parameter, "^beta0_pelagic\\[")|
           str_detect(Parameter, "^beta1_pelagic\\[")|
           str_detect(Parameter, "^beta2_pelagic\\[")|
           str_detect(Parameter, "^beta3_pelagic\\[")|
           str_detect(Parameter, "^beta0_yellow\\[")|
           str_detect(Parameter, "^beta1_yellow\\[")|
           str_detect(Parameter, "^beta2_yellow\\[")|
           str_detect(Parameter, "^beta3_yellow\\[")|
           str_detect(Parameter, "^beta0_black\\[")|
           str_detect(Parameter, "^beta2_black\\[")|
           str_detect(Parameter, "^beta3_black\\[")|
           str_detect(Parameter, "^beta4_black\\[")|
           str_detect(Parameter, "^beta0_dsr\\[")|
           str_detect(Parameter, "^beta1_dsr\\[")|
           str_detect(Parameter, "^beta2_dsr\\[")|
           str_detect(Parameter, "^beta3_dsr\\[")|
           str_detect(Parameter, "^beta4_dsr\\[")|
           str_detect(Parameter, "^beta0_slope\\[")|
           str_detect(Parameter, "^beta1_slope\\[")|
           str_detect(Parameter, "^beta2_slope\\[")|
           str_detect(Parameter, "^beta3_slope\\[")|
           str_detect(Parameter, "^beta4_slope\\[")|
           str_detect(Parameter, "^sigma_H\\[")|
           str_detect(Parameter, "^beta_H\\[")|
           str_detect(Parameter, "^beta0_H\\[")|
           str_detect(Parameter, "^lambda_H\\[")|
           str_detect(Parameter, "^mu_lambda_H\\[")|
           str_detect(Parameter, "^sigma_lambda_H\\["))

Fig_N <- 0
Tab_N <- 0
App_N <- 0
AT_N <- 1

southeast <- c("CSEO","EWYKT","NSEI","NSEO","SSEI","SSEO")
central <- c("CI","NG","PWSI","PWSO")
kodiak <- c("BSAI","SOKO2SAP","WKMA","afognak","eastside","northeast")

# Separate out everything for plotting:


# MAking greek characters:
library(officer)
library(flextable)

make_param_label <- function(code) {
  greek_map <- list("m" = "μ", "s" = "σ", "b" = "β", "l" = "λ")

  greek <- greek_map[[substr(code, 1, 1)]]
  subscript <- substr(code, 2, nchar(code))

  if (is.null(greek)) {
    # fallback: just return code as-is
    return(as_paragraph(as_chunk(code)))
  }

  as_paragraph(
    as_chunk(greek),
    as_chunk(subscript, props = fp_text(vertical.align = "subscript"))
  )
}

format_numbers <- function(df) {
  df %>%
    mutate(across(where(is.numeric), ~ case_when(
      . > 10  ~ formatC(., format = "f", big.mark = ",", digits = 0),  # Whole number with commas
      . <= 10 ~ formatC(., format = "f", digits = 3),  # 3 decimal places, no scientific notation
      TRUE ~ as.character(.)
    )))
}

```

# Appendices

<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

**Appendix A: Spline fomulae:** The following formulas were used to fit the penalized spline to the harvest trend in the model. In region *R* parameters $\alpha_{\lambda_R}$ and $\beta_{\lambda_R}$ were calculated as

$\alpha_{\lambda_R}~=~\frac{\mu_{\lambda_R}^2}{\sigma_{\lambda_R}^2}$

$\beta_{\lambda_R}~=~\frac{\mu_{\lambda_R}}{\sigma_{\lambda_R}^2}$

where $\mu_{\lambda_R}$ and $\sigma_{\lambda_R}$ were derived from priors (Table PRIORS1). 

The harvest trend spline by area, *a*, was modeled such that $\lambda_a$ was derived from the regional $\alpha_{\lambda_R}$ and $\beta_{\lambda_R}$ parameters based on a gamma distribution such that

$\lambda_a~\sim~gamma(\alpha_{\lambda_R}, \beta_{\lambda_R})$

Area specific $\beta_{a,1:C}$ matrices with *a* by *C* dimensions where *C* is equal to the  number of knots in the spline were derived from a multivariate normal distribution such that

$\beta_{a,1:C}~\sim~mnorm(zero_{1:C} + \beta0_a, \lambda_a * Q_{1:C,1:C})$

where $beta0_a$ was derived from a prior (Table PRIORS1), $zero_{1:C}$ is a vector of zeros and $Q_{1:C,1:C}$ is a matrix derived from the number of knots (see https://bragqut.github.io/2016/05/24/samclifford-splines/ for original formulation and the model code in https://github.com/ADFG-DSF/RockfishSportMort/tree/main/models). 

The true harvest in area *a* and year *y*, $H_{ay}$, was fit to the spline trend line such that

$log(H_{ay}) ~\sim~ norm(H_{ay}^{trend}, \tau_a)$ 

where

$\tau_a ~=~ \frac{1}{\sigma_{Ha}}$

and $\sigma_{Ha}$ was derived from a prior distribution (Table PRIORS1). The spine trend $H_{ay}^{trend}$ was calculated as 

$H_{ay}^{trend} ~=~ Z_y * \beta_{a,1:C}$

where $Z_y$ is a matrix derived from the number of knots and the number of years in the time series (see https://bragqut.github.io/2016/05/24/samclifford-splines/ for original formulation and the model code in https://github.com/ADFG-DSF/RockfishSportMort/tree/main/models).

<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

# Appendix B: Model fit to weight data.

<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

```{r, fig.width = 10, fig.height = 10, fig.cap = paste0("**Appenidx B",App_N,".**- Mean weights of black rockfish used to estimate biomass from harvest and release mortality estimates in numbers of fish.")}
pal <- wes_palette(name = "Moonrise2", n=3)

brf_wt_mod <- 
  rbind(postH$mean$wt[,,1,1] %>% t(), #area,year,user,species
        postH$mean$wt[,,2,1] %>% t()) %>%
  as.data.frame() %>%
  setNames(nm = unique(H_ayg$area)) %>%
  mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "model") %>%
  pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt")  %>%
  mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)) %>%
  left_join(rbind(postH$q2.5$wt[,,1,1] %>% t(),
                  postH$q2.5$wt[,,2,1] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "w_lo95")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source")) %>%
  left_join(rbind(postH$q97.5$wt[,,1,1] %>% t(),
                  postH$q97.5$wt[,,2,1] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "w_hi95")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source")) %>%
  left_join(rbind(postH$sd$wt[,,1,1] %>% t(),
                  postH$sd$wt[,,2,1] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "sd_wt")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source"))
brf_wt_obs <- 
  as.data.frame(
    rbind(cbind(t(jags_dat$r2_gwt_b),t(jags_dat$r1_gwt_b)),
          cbind(t(jags_dat$r2_uwt_b),t(jags_dat$r1_uwt_b)))) %>%
  setNames(nm = unique(H_ayg$area)) %>%
  mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "port samples") %>%
  pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt") %>%
  mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE))  %>% 
  left_join(
    as.data.frame(
    rbind(cbind(t(jags_dat$r2_gwtcv_b),t(jags_dat$r1_gwtcv_b)),
          cbind(t(jags_dat$r2_uwtcv_b),t(jags_dat$r1_uwtcv_b)))) %>%
    setNames(nm = unique(H_ayg$area)) %>%
    mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "samples") %>%
    pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt_cv"),
    by = c("year","user","source","area")
  ) %>%
  filter(!is.na(wt)) %>%
  mutate(lo_95 = wt - wt * (1.95 * wt_cv),
         hi_95 = wt + wt * (1.95 * wt_cv),
         area = factor(area, unique(H_ayg$area), ordered = TRUE))
  
brf_wt_mod %>% #filter(user != "all") %>%
  ggplot(aes(x = year, y = wt, color = user, shape = source)) +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) +
  geom_ribbon(aes(ymin = w_lo95, ymax = w_hi95, fill = user), 
              alpha = 0.2, color = NA) +
  #geom_point(aes(shape = source)) + 
  geom_line() + geom_point(alpha = 0.5, size = 0.5) +
  geom_point(data  = brf_wt_obs, size = 2) +
  facet_wrap(. ~ area) +
  scale_shape_manual(values = c(18, 10)) + theme_bw(base_size = 14)+
  theme (axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
         legend.position = "bottom") +
  labs(y = "Wt (lbs)", x = "Year")

App_N <- App_N + 1

``` 
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

```{r, fig.width = 10, fig.height = 10, fig.cap = paste0("**Appenidx B",App_N,".**- Mean weights of yelloweye rockfish used to estimate biomass from harvest and release mortality estimates in numbers of fish.")}
pal <- wes_palette(name = "Moonrise2", n=3)

ye_wt_mod <- 
  rbind(postH$mean$wt[,,1,2] %>% t(), #area,year,user,species
        postH$mean$wt[,,2,2] %>% t()) %>%
  as.data.frame() %>%
  setNames(nm = unique(H_ayg$area)) %>%
  mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "model") %>%
  pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt")  %>%
  mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)) %>%
  left_join(rbind(postH$q2.5$wt[,,1,2] %>% t(),
                  postH$q2.5$wt[,,2,2] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "w_lo95")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source")) %>%
  left_join(rbind(postH$q97.5$wt[,,1,2] %>% t(),
                  postH$q97.5$wt[,,2,2] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "w_hi95")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source")) %>%
  left_join(rbind(postH$sd$wt[,,1,2] %>% t(),
                  postH$sd$wt[,,2,2] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "sd_wt")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source"))
ye_wt_obs <- 
  as.data.frame(
    rbind(cbind(t(jags_dat$r2_gwt_y),t(jags_dat$r1_gwt_y)),
          cbind(t(jags_dat$r2_uwt_y),t(jags_dat$r1_uwt_y)))) %>%
  setNames(nm = unique(H_ayg$area)) %>%
  mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "port samples") %>%
  pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt") %>%
  mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE))  %>% 
  left_join(
    as.data.frame(
    rbind(cbind(t(jags_dat$r2_gwtcv_y),t(jags_dat$r1_gwtcv_y)),
          cbind(t(jags_dat$r2_uwtcv_y),t(jags_dat$r1_uwtcv_y)))) %>%
    setNames(nm = unique(H_ayg$area)) %>%
    mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "samples") %>%
    pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt_cv"),
    by = c("year","user","source","area")
  ) %>%
  filter(!is.na(wt)) %>%
  mutate(lo_95 = wt - wt * (1.95 * wt_cv),
         hi_95 = wt + wt * (1.95 * wt_cv),
         area = factor(area, unique(H_ayg$area), ordered = TRUE))
  
ye_wt_mod %>% #filter(user != "all") %>%
  ggplot(aes(x = year, y = wt, color = user, shape = source)) +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) +
  geom_ribbon(aes(ymin = w_lo95, ymax = w_hi95, fill = user), 
              alpha = 0.2, color = NA) +
  #geom_point(aes(shape = source)) + 
  geom_line() + geom_point(alpha = 0.5, size = 0.5) +
  geom_point(data  = ye_wt_obs, size = 2) +
  facet_wrap(. ~ area) +
  scale_shape_manual(values = c(18, 10)) + theme_bw(base_size = 14)+
  theme (axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
         legend.position = "bottom") +
  labs(y = "Wt (lbs)", x = "Year")

App_N <- App_N + 1

``` 
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage


```{r, fig.width = 8, fig.height = 4, fig.cap = paste0("**Appenidx B",App_N,".**- Mean weights of non-black, pelagic rockfish used to estimate biomass from harvest and release mortality estimates in numbers of fish.")}
pal <- wes_palette(name = "Moonrise2", n=3)

pel_wt_mod <- 
  rbind(postH$mean$wt[,,1,3] %>% t(), #area,year,user,species
        postH$mean$wt[,,2,3] %>% t()) %>%
  as.data.frame() %>%
  setNames(nm = unique(H_ayg$area)) %>%
  mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "model") %>%
  pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt")  %>%
  mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)) %>%
  left_join(rbind(postH$q2.5$wt[,,1,3] %>% t(),
                  postH$q2.5$wt[,,2,3] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "w_lo95")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source")) %>%
  left_join(rbind(postH$q97.5$wt[,,1,3] %>% t(),
                  postH$q97.5$wt[,,2,3] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "w_hi95")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source")) %>%
  left_join(rbind(postH$sd$wt[,,1,3] %>% t(),
                  postH$sd$wt[,,2,3] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "sd_wt")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source"))
pel_wt_obs <- 
  as.data.frame(
    rbind(cbind(t(jags_dat$r1_gwt_p)),
          cbind(t(jags_dat$r1_uwt_p)))) %>%
  setNames(nm = unique(H_ayg$area)[11:16]) %>%
  mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "port samples") %>%
  pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt") %>%
  mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE))  %>% 
  left_join(
    as.data.frame(
    rbind(cbind(t(jags_dat$r1_gwtcv_p)),
          cbind(t(jags_dat$r1_uwtcv_p)))) %>%
    setNames(nm = unique(H_ayg$area)[11:16]) %>%
    mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "samples") %>%
    pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt_cv"),
    by = c("year","user","source","area")
  ) %>%
  filter(!is.na(wt)) %>%
  mutate(lo_95 = wt - wt * (1.95 * wt_cv),
         hi_95 = wt + wt * (1.95 * wt_cv),
         area = factor(area, unique(H_ayg$area), ordered = TRUE))

southeast <- c("CSEO","EWYKT","NSEI","NSEO","SSEI","SSEO")

pel_wt_mod %>% filter(area %in% southeast) %>%
  ggplot(aes(x = year, y = wt, color = user, shape = source)) +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) +
  geom_ribbon(aes(ymin = w_lo95, ymax = w_hi95, fill = user), 
              alpha = 0.2, color = NA) +
  #geom_point(aes(shape = source)) + 
  geom_line() + geom_point(alpha = 0.5, size = 0.5) +
  geom_point(data  = pel_wt_obs, size = 2) +
  facet_wrap(. ~ area) +
  scale_shape_manual(values = c(18, 10)) + theme_bw(base_size = 14)+
  theme (axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  labs(y = "Wt (lbs)", x = "Year")

App_N <- App_N + 1

``` 
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage


```{r, fig.width = 8, fig.height = 4, fig.cap = paste0("**Appenidx B",App_N,".**- Mean weights of non-yelloweye, demersal shelf rockfish used to estimate biomass from harvest and release mortality estimates in numbers of fish.")}
pal <- wes_palette(name = "Moonrise2", n=3)

dsr_wt_mod <- 
  rbind(postH$mean$wt[,,1,4] %>% t(), #area,year,user,species
        postH$mean$wt[,,2,4] %>% t()) %>%
  as.data.frame() %>%
  setNames(nm = unique(H_ayg$area)) %>%
  mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "model") %>%
  pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt")  %>%
  mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)) %>%
  left_join(rbind(postH$q2.5$wt[,,1,4] %>% t(),
                  postH$q2.5$wt[,,2,4] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "w_lo95")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source")) %>%
  left_join(rbind(postH$q97.5$wt[,,1,4] %>% t(),
                  postH$q97.5$wt[,,2,4] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "w_hi95")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source")) %>%
  left_join(rbind(postH$sd$wt[,,1,4] %>% t(),
                  postH$sd$wt[,,2,4] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "sd_wt")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source"))
dsr_wt_obs <- 
  as.data.frame(
    rbind(cbind(t(jags_dat$r1_gwt_d)),
          cbind(t(jags_dat$r1_uwt_d)))) %>%
  setNames(nm = unique(H_ayg$area)[11:16]) %>%
  mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "port samples") %>%
  pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt") %>%
  mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE))  %>% 
  left_join(
    as.data.frame(
    rbind(cbind(t(jags_dat$r1_gwtcv_d)),
          cbind(t(jags_dat$r1_uwtcv_d)))) %>%
    setNames(nm = unique(H_ayg$area)[11:16]) %>%
    mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "samples") %>%
    pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt_cv"),
    by = c("year","user","source","area")
  ) %>%
  filter(!is.na(wt)) %>%
  mutate(lo_95 = wt - wt * (1.95 * wt_cv),
         hi_95 = wt + wt * (1.95 * wt_cv),
         area = factor(area, unique(H_ayg$area), ordered = TRUE))

southeast <- c("CSEO","EWYKT","NSEI","NSEO","SSEI","SSEO")

dsr_wt_mod %>% filter(area %in% southeast) %>%
  ggplot(aes(x = year, y = wt, color = user, shape = source)) +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) +
  geom_ribbon(aes(ymin = w_lo95, ymax = w_hi95, fill = user), 
              alpha = 0.2, color = NA) +
  #geom_point(aes(shape = source)) + 
  geom_line() + geom_point(alpha = 0.5, size = 0.5) +
  geom_point(data  = dsr_wt_obs, size = 2) +
  facet_wrap(. ~ area) +
  scale_shape_manual(values = c(18, 10)) + theme_bw(base_size = 14)+
  theme (axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  labs(y = "Wt (lbs)", x = "Year")

App_N <- App_N + 1

``` 
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage


```{r, fig.width = 8, fig.height = 4, fig.cap = paste0("**Appenidx B",App_N,".**- Mean weights of slope rockfish used to estimate biomass from harvest and release mortality estimates in numbers of fish.")}
pal <- wes_palette(name = "Moonrise2", n=3)

slope_wt_mod <- 
  rbind(postH$mean$wt[,,1,5] %>% t(), #area,year,user,species
        postH$mean$wt[,,2,5] %>% t()) %>%
  as.data.frame() %>%
  setNames(nm = unique(H_ayg$area)) %>%
  mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "model") %>%
  pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt")  %>%
  mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)) %>%
  left_join(rbind(postH$q2.5$wt[,,1,5] %>% t(),
                  postH$q2.5$wt[,,2,5] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "w_lo95")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source")) %>%
  left_join(rbind(postH$q97.5$wt[,,1,5] %>% t(),
                  postH$q97.5$wt[,,2,5] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "w_hi95")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source")) %>%
  left_join(rbind(postH$sd$wt[,,1,5] %>% t(),
                  postH$sd$wt[,,2,5] %>% t()) %>%
              as.data.frame() %>%
              setNames(nm = unique(H_ayg$area)) %>%
              mutate(year = rep(unique(Hhat_ay$year), times = 2),
                     user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
                     source = "model") %>%
              pivot_longer(-c(year, user,source), names_to = "area", values_to = "sd_wt")  %>%
              mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE)),
            by = c("year","area","user","source"))
slope_wt_obs <- 
  as.data.frame(
    rbind(cbind(t(jags_dat$r1_gwt_s)),
          cbind(t(jags_dat$r1_uwt_s)))) %>%
  setNames(nm = unique(H_ayg$area)[11:16]) %>%
  mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "port samples") %>%
  pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt") %>%
  mutate(area = factor(area, unique(H_ayg$area), ordered = TRUE))  %>% 
  left_join(
    as.data.frame(
    rbind(cbind(t(jags_dat$r1_gwtcv_s)),
          cbind(t(jags_dat$r1_uwtcv_s)))) %>%
    setNames(nm = unique(H_ayg$area)[11:16]) %>%
    mutate(year = rep(unique(Hhat_ay$year), times = 2),
         user = rep(c("charter", "private"), each = length(unique(Hhat_ay$year))),
         source = "samples") %>%
    pivot_longer(-c(year, user,source), names_to = "area", values_to = "wt_cv"),
    by = c("year","user","source","area")
  ) %>%
  filter(!is.na(wt)) %>%
  mutate(lo_95 = wt - wt * (1.95 * wt_cv),
         hi_95 = wt + wt * (1.95 * wt_cv),
         area = factor(area, unique(H_ayg$area), ordered = TRUE))

southeast <- c("CSEO","EWYKT","NSEI","NSEO","SSEI","SSEO")

slope_wt_mod %>% filter(area %in% southeast) %>%
  ggplot(aes(x = year, y = wt, color = user, shape = source)) +
  scale_fill_manual(values = pal) +
  scale_color_manual(values = pal) +
  geom_ribbon(aes(ymin = w_lo95, ymax = w_hi95, fill = user), 
              alpha = 0.2, color = NA) +
  #geom_point(aes(shape = source)) + 
  geom_line() + geom_point(alpha = 0.5, size = 0.5) +
  geom_point(data  = slope_wt_obs, size = 2) +
  facet_wrap(. ~ area) +
  scale_shape_manual(values = c(18, 10)) + theme_bw(base_size = 14)+
  theme (axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  labs(y = "Wt (lbs)", x = "Year")

App_N <- App_N + 1

``` 
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

# Appendix C: Model output harvest, release, release mortality and total removal estimates 

<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

**Appendix C`r AT_N`.** Black rockfish harvest, release, release mortality, weight, and total mortality estimates by year and user group for Cook Inlet Commercial Fisheries Management Unit 1977 - 2023. User "gui" indicates guided trips while "pri" indicates unguided trips. Harvest, release and release mortalities are estimated in numbers of fish. 

```{r}
black <- readxl::read_xlsx(paste0("RF_Sport_Removals_RepV.xlsx"), 
                       sheet = "Black") %>% 
  clean_names() %>% filter(rowSums(is.na(.)) < ncol(.)) %>%
  mutate(p_mort_r = round(p_mort_r,3),
         mort_rate = round(mort_rate,3),
         year = as.factor(year),
         user = ifelse(user == "guided","gui",
                       ifelse(user == "unguided","pri","All"))) 

black <- format_numbers(black)

black <- black %>%
  mutate(r_lo95 = ifelse(as.numeric(gsub(",", "", r_lo95)) <= 10,
                         round(as.numeric(r_lo95),0),
                         r_lo95),
         #r_hi95 = round(as.numeric(r_hi95),0),
         rm_lo95 = ifelse(as.numeric(gsub(",", "", rm_lo95)) <= 10,
                         round(as.numeric(rm_lo95),0),
                         rm_lo95),
         rm_hi95 = ifelse(as.numeric(gsub(",", "", rm_hi95)) <= 10,
                         round(as.numeric(rm_lo95),0),
                         rm_hi95),
         release_morts = round(as.numeric(release_morts),0),
         #harvests = paste0(harvests, " (",sd_h,")"),
         #releases = paste0(releases, " (",sd_r,")"),
         #release_morts = paste0(release_morts, " (",sd_rm,")"),
         #wt = paste0(wt, " (",sd_wt,")"),
         #mort_lbs = paste0(mort_lbs, " (",sd_m,")")
         'H. 95% CI' = paste0(h_lo95, " - ", h_hi95),
         'R. 95% CI' = paste0(r_lo95, " - ", r_hi95),
         'RM. 95% CI' = paste0(rm_lo95, " - ", rm_hi95),
         'TM. 95% CI' = paste0(m_lo95, " - ", m_hi95)
         ) %>%
  
  select(Year = year, User = user, area,region,
         'Harvest' = harvests, 'H. SD' =  sd_h, 'H. 95% CI',  #'H. lower 95%' = h_lo95, 'H. upper 95%' = h_hi95,
         'Releases' = releases, 'R. SD' =  sd_r, 'R. 95% CI', #'R. lower 95%' = r_lo95, 'R. upper 95%' = r_hi95,
  ##       'Rel. Morts' = release_morts, 'RM. SD' =  sd_rm, 'RM. 95% CI', #'RM. lower 95%' = rm_lo95, 'RM. upper 95%' = rm_hi95,
         'Rel. Mort. Rate' = mort_rate, 'Mean wt lbs' = wt, #'wt. SD' =  sd_wt,
         'Total Mortality (lbs)' = mort_lbs, 'TM. SD' =  sd_m,  'TM. 95% CI'#, 'TM. lower 95%' = m_lo95, 'TM. upper 95%' = m_hi95
         ) #%>%
         #"Prop. mortality from releases" = p_mort_r) %>%
#  select(-c(p_mort_h,p_mort_r,
            #sd_h,sd_r,sd_rm,sd_wt,sd_m,
#            h_lo95,h_hi95, r_lo95,r_hi95, rm_lo95,rm_hi95, m_lo95,m_hi95))

black %>% filter(area == "CI" & User != "All") %>%
  select(-region, -area)-> black_ci

flextable(black_ci) %>%
  add_header_row(values = c("Cook Inlet Black Rockfish"), colwidths = c(13)) %>%
  #autofit() %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "header") %>%
  fontsize(size = 9, part = "body") %>%
  align(j = 1:13, align = "center", part = "all") %>%
  #set_table_properties(width = 1, layout = "autofit") %>%
  set_table_properties(layout = "fixed") %>%
  line_spacing(space = 0.5, part = "body") %>% 
  height_all(height = 0.10) %>%
  width(j = c(1:2,4,7,9:10,12), width = 0.53) %>%
  width(j = c(3,6,11), width = 0.70) %>%
  width(j = c(5,8,13), width = 1.06) 

AT_N <- AT_N + 1

#7*0.53 + 3*0.70 + 3*1.06

```
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

**Appendix C`r AT_N`.** Black rockfish harvest, release, release mortality, weight, and total mortality estimates by year and user group for North Gulf Commercial Fisheries Management Unit 1977 - 2023. User "gui" indicates guided trips while "pri" indicates unguided trips. Harvest, release and release mortalities are estimated in numbers of fish. 

```{r}

flextable(black %>% filter(area == "NG" & User != "All") %>%
  select(-region, -area)) %>%
  add_header_row(values = c("North Gulf Black Rockfish"), colwidths = c(13)) %>%
  #autofit() %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "header") %>%
  fontsize(size = 9, part = "body") %>%
  align(j = 1:13, align = "center", part = "all") %>%
  #set_table_properties(width = 1, layout = "autofit") %>%
  set_table_properties(layout = "fixed") %>%
  line_spacing(space = 0.5, part = "body") %>% 
  height_all(height = 0.10) %>%
  width(j = c(1:2,4,7,9:10,12), width = 0.53) %>%
  width(j = c(3,6,11), width = 0.70) %>%
  width(j = c(5,8,13), width = 1.06) 

AT_N <- AT_N + 1

```
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

**Appendix C`r AT_N`.** Black rockfish harvest, release, release mortality, weight, and total mortality estimates by year and user group for Prince William Sound Inside Commercial Fisheries Management Unit 1977 - 2023. User "gui" indicates guided trips while "pri" indicates unguided trips. Harvest, release and release mortalities are estimated in numbers of fish. 

```{r}

flextable(black %>% filter(area == "PWSI" & User != "All") %>%
  select(-region, -area)) %>%
  add_header_row(values = c("Prince William Sound Inside Black Rockfish"), colwidths = c(13)) %>%
  #autofit() %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "header") %>%
  fontsize(size = 9, part = "body") %>%
  align(j = 1:13, align = "center", part = "all") %>%
  #set_table_properties(width = 1, layout = "autofit") %>%
  set_table_properties(layout = "fixed") %>%
  line_spacing(space = 0.5, part = "body") %>% 
  height_all(height = 0.10) %>%
  width(j = c(1:2,4,7,9:10,12), width = 0.53) %>%
  width(j = c(3,6,11), width = 0.70) %>%
  width(j = c(5,8,13), width = 1.06) 

AT_N <- AT_N + 1

```
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

**Appendix C`r AT_N`.** Black rockfish harvest, release, release mortality, weight, and total mortality estimates by year and user group for Prince William Sound Outside Commercial Fisheries Management Unit 1977 - 2023. User "gui" indicates guided trips while "pri" indicates unguided trips. Harvest, release and release mortalities are estimated in numbers of fish. 

```{r}

flextable(black %>% filter(area == "PWSO" & User != "All") %>%
  select(-region, -area)) %>%
  add_header_row(values = c("Prince William Sound Outside Black Rockfish"), colwidths = c(13)) %>%
  #autofit() %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "header") %>%
  fontsize(size = 9, part = "body") %>%
  align(j = 1:13, align = "center", part = "all") %>%
  #set_table_properties(width = 1, layout = "autofit") %>%
  set_table_properties(layout = "fixed") %>%
  line_spacing(space = 0.5, part = "body") %>% 
  height_all(height = 0.10) %>%
  width(j = c(1:2,4,7,9:10,12), width = 0.53) %>%
  width(j = c(3,6,11), width = 0.70) %>%
  width(j = c(5,8,13), width = 1.06) 

AT_N <- AT_N + 1

```
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

**Appendix C`r AT_N`.** Black rockfish harvest, release, release mortality, weight, and total mortality estimates by year and user group for Bering Sea & Aleutian Islands Commercial Fisheries Management Units 1977 - 2023. User "gui" indicates guided trips while "pri" indicates unguided trips. Harvest, release and release mortalities are estimated in numbers of fish. 

```{r}

#unique(black$area)

flextable(black %>% filter(area == "BSAI" & User != "All") %>%
  select(-region, -area)) %>%
  add_header_row(values = c("Bering Sea & Aleutian Islands Black Rockfish"), colwidths = c(13)) %>%
  #autofit() %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "header") %>%
  fontsize(size = 9, part = "body") %>%
  align(j = 1:13, align = "center", part = "all") %>%
  #set_table_properties(width = 1, layout = "autofit") %>%
  set_table_properties(layout = "fixed") %>%
  line_spacing(space = 0.5, part = "body") %>% 
  height_all(height = 0.10) %>%
  width(j = c(1:2,4,7,9:10,12), width = 0.53) %>%
  width(j = c(3,6,11), width = 0.70) %>%
  width(j = c(5,8,13), width = 1.06) 

AT_N <- AT_N + 1

```
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

**Appendix C`r AT_N`.** Black rockfish harvest, release, release mortality, weight, and total mortality estimates by year and user group for the Southeast, Southwest, Chignik and South Alaska Peninsula (SAKPEN) districts (SOKO2SAP) 1977 - 2023. User "gui" indicates guided trips while "pri" indicates unguided trips. Harvest, release and release mortalities are estimated in numbers of fish. 

```{r}

#unique(black$area)

flextable(black %>% filter(area == "SOKO2SAP" & User != "All") %>%
  select(-region, -area)) %>%
  add_header_row(values = c("Southeast, Southwest (Kodiak), Chignik and South Alaska Peninsula (SAKPEN) Black Rockfish"), colwidths = c(13)) %>%
  #autofit() %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "header") %>%
  fontsize(size = 9, part = "body") %>%
  align(j = 1:13, align = "center", part = "all") %>%
  #set_table_properties(width = 1, layout = "autofit") %>%
  set_table_properties(layout = "fixed") %>%
  line_spacing(space = 0.5, part = "body") %>% 
  height_all(height = 0.10) %>%
  width(j = c(1:2,4,7,9:10,12), width = 0.53) %>%
  width(j = c(3,6,11), width = 0.70) %>%
  width(j = c(5,8,13), width = 1.06) 

AT_N <- AT_N + 1

```
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

**Appendix C`r AT_N`.** Black rockfish harvest, release, release mortality, weight, and total mortality estimates by year and user group for the Westside and Mainland districts (WKMA) 1977 - 2023. User "gui" indicates guided trips while "pri" indicates unguided trips. Harvest, release and release mortalities are estimated in numbers of fish. 

```{r}

#unique(black$area)

flextable(black %>% filter(area == "WKMA" & User != "All") %>%
  select(-region, -area)) %>%
  add_header_row(values = c("Westside and Mainland Kodiak districts Black Rockfish"), colwidths = c(13)) %>%
  #autofit() %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "header") %>%
  fontsize(size = 9, part = "body") %>%
  align(j = 1:13, align = "center", part = "all") %>%
  #set_table_properties(width = 1, layout = "autofit") %>%
  set_table_properties(layout = "fixed") %>%
  line_spacing(space = 0.5, part = "body") %>% 
  height_all(height = 0.10) %>%
  width(j = c(1:2,4,7,9:10,12), width = 0.53) %>%
  width(j = c(3,6,11), width = 0.70) %>%
  width(j = c(5,8,13), width = 1.06) 

AT_N <- AT_N + 1

```
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

**Appendix C`r AT_N`.** Black rockfish harvest, release, release mortality, weight, and total mortality estimates by year and user group for the Afognak Commercial Fisheries Management Unit 1977 - 2023. User "gui" indicates guided trips while "pri" indicates unguided trips. Harvest, release and release mortalities are estimated in numbers of fish. 

```{r}

#unique(black$area)

flextable(black %>% filter(area == "AFOGNAK" & User != "All") %>%
  select(-region, -area)) %>%
  add_header_row(values = c("Afognak (Kodiak) Black Rockfish"), colwidths = c(13)) %>%
  #autofit() %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "header") %>%
  fontsize(size = 9, part = "body") %>%
  align(j = 1:13, align = "center", part = "all") %>%
  #set_table_properties(width = 1, layout = "autofit") %>%
  set_table_properties(layout = "fixed") %>%
  line_spacing(space = 0.5, part = "body") %>% 
  height_all(height = 0.10) %>%
  width(j = c(1:2,4,7,9:10,12), width = 0.53) %>%
  width(j = c(3,6,11), width = 0.70) %>%
  width(j = c(5,8,13), width = 1.06) 

AT_N <- AT_N + 1

```
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

**Appendix C`r AT_N`.** Black rockfish harvest, release, release mortality, weight, and total mortality estimates by year and user group for the Eastside Kodiak Commercial Fisheries Management Unit 1977 - 2023. User "gui" indicates guided trips while "pri" indicates unguided trips. Harvest, release and release mortalities are estimated in numbers of fish. 

```{r}

#unique(black$area)

flextable(black %>% filter(area == "EASTSIDE" & User != "All") %>%
  select(-region, -area)) %>%
  add_header_row(values = c("Eastside Kodiak Black Rockfish"), colwidths = c(13)) %>%
  #autofit() %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "header") %>%
  fontsize(size = 9, part = "body") %>%
  align(j = 1:13, align = "center", part = "all") %>%
  #set_table_properties(width = 1, layout = "autofit") %>%
  set_table_properties(layout = "fixed") %>%
  line_spacing(space = 0.5, part = "body") %>% 
  height_all(height = 0.10) %>%
  width(j = c(1:2,4,7,9:10,12), width = 0.53) %>%
  width(j = c(3,6,11), width = 0.70) %>%
  width(j = c(5,8,13), width = 1.06) 

AT_N <- AT_N + 1

```
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage

**Appendix C`r AT_N`.** Black rockfish harvest, release, release mortality, weight, and total mortality estimates by year and user group for the Eastside Kodiak Commercial Fisheries Management Unit 1977 - 2023. User "gui" indicates guided trips while "pri" indicates unguided trips. Harvest, release and release mortalities are estimated in numbers of fish. 

```{r}

#unique(black$area)

flextable(black %>% filter(area == "NORTHEAST" & User != "All") %>%
  select(-region, -area)) %>%
  add_header_row(values = c("Northeast Kodiak Black Rockfish"), colwidths = c(13)) %>%
  #autofit() %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 10, part = "header") %>%
  fontsize(size = 9, part = "body") %>%
  align(j = 1:13, align = "center", part = "all") %>%
  #set_table_properties(width = 1, layout = "autofit") %>%
  set_table_properties(layout = "fixed") %>%
  line_spacing(space = 0.5, part = "body") %>% 
  height_all(height = 0.10) %>%
  width(j = c(1:2,4,7,9:10,12), width = 0.53) %>%
  width(j = c(3,6,11), width = 0.70) %>%
  width(j = c(5,8,13), width = 1.06) 

AT_N <- AT_N + 1

```
<div style="text-align:left; width: 70%; margin: auto;"> </div>
\newpage








